---
title: "Visualizing a network"


output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#You can use the following function to clean your Rstudio environment  
```{r}
rm(list=ls())
```

```{r, message=FALSE, warning=FALSE}
install.packages('ggraph')
library(ggraph)
library(igraph)
```

```{r}
ggraph:::igraphlayouts
```

#Network analysis example

```{r}
df <- data.frame(
  A = c("Berlin", "Amsterdam", "New York") , 
  B = c("Munich", "Utrecht", "Chicago"))
```


```{r}
df.g <- graph_from_data_frame (d = df, directed = FALSE)
```


```{r}
plot(df.g, vertex.label = V(df.g)$name)
```


```{r}
df.g %>%
  ggraph(layout = "fr") +
  geom_node_text(aes(label=V(df.g)$name ), size = 3) +
  geom_edge_diagonal(color = "black", alpha = 0.5)
  geom_edge_link(aes(edge_alpha = 0.5))
```


## Airbnb Example

#Load the libraries
```{r}
library(dplyr)
library(tidyr)
library(tidytext)
library(tidyverse)
```

#read in the data
```{r}
reviews_original <- read_csv("asheville_reviews.csv")
```

```{r}
reviews <-reviews_original   %>% 
  select (listing_id, comment_id=id,date ,reviewer_id,reviewer_name, comments)
```


# tokenize and pre-process the text (n=2)

note: the code below may take few minutes to run
```{r}
reviews_bigrams <- reviews %>%
  unnest_tokens(bigram, comments, token = "ngrams", n = 2)%>%
  separate(bigram, c("word1", "word2"), sep = " ")%>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)
```

# count the bigrams
```{r}
bigram_counts <- reviews_bigrams %>% 
  count(word1, word2, sort = TRUE)

bigram_counts
```


### Visualizing a network of bigrams

```{r, message=FALSE, warning=FALSE}
#install.packages("igraph")
library(igraph)
```

# filter for only relatively common combinations
```{r}
bigram_graph <- bigram_counts %>%
  filter(n > 500) %>%
  graph_from_data_frame()

bigram_graph
```


We can convert an igraph object into a ggraph with the ggraph function.
```{r, warning=FALSE, message=FALSE}
#install.packages("ggraph")
library(ggraph)
```

For a basic graph, we need to include the following layers: nodes, edges, and text.

There are different networks layouts in a plot that can make them more readable. To see a list of possible layouts you can run:

```{r}
#ggraph:::igraphlayouts
```


```{r}
set.seed(2017)
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
```

The results show us some details of the text structure.

we can polish the graph by including some short statements:

edges: showing directions with an arrow the end_cap option - tells the arrow to end before touching the node 
nodes: show nodes with light blue points
add a theme to the plot:

```{r}
set.seed(2016)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n,edge_width=n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```


You may need to go through some iterations to get your plots into a nice format

You can show edges as lines. For that you need to add a statement "directed = FALSE" to the function "graph_from_data_frame()"

```{r}
bigram_graph <- bigram_counts %>%
  filter(n > 1000) %>%
  graph_from_data_frame(directed = FALSE)

set.seed(2016)

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n,edge_width=n), show.legend = FALSE,
                 end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```

make the graph even look better:

```{r}
bigram_graph <- bigram_counts %>%
  filter(n > 1000) %>%
  graph_from_data_frame(directed = FALSE)

set.seed(2016)
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") +
  geom_node_point(size=1) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)+
  theme_void()
```


